### 2015-01-11 paper/Content/03conclusion.tex
Conclusion URLs

There are further and particularly similar MVP approaches developed and provided by the \emph{Android} developer community. 
\emph{Google} developer \emph{Chris Banes} has developed the \emph{Android} app \emph{philm} basing on MVP. 
The very demonstrative source code is offered on \emph{github} [https://github.com/chrisbanes/philm] and worth seeing. 
Moreover there is a huge developer community on \emph{Google+} [https://plus.google.com/communities/114285790907815804707] dealing with different MVP approaches. 
Finally, we want to draw your attention to the paper \emph{Android Passive MVC: a Novel Architecture Model for Android Application Development} 
[Quelle] which is worth reading and has been an inspiration for our approach. Although the paper proposes an architecture which is rather MVC than MVP-based, 
it offers an interesting approach how the components of an \emph{Android} app can be organized for building an MV-x structure.

>>>>

There are further and particularly similar MVP approaches developed and provided by the \emph{Android} developer community. 
\emph{Google} developer \emph{Chris Banes} has developed the \emph{Android} app \emph{philm} basing on MVP. 
The very demonstrative source code\footnote{\emph{philm} source code: \\\url{https://github.com/chrisbanes/philm}} is offered on \emph{github} and worth seeing. 
Moreover there is a huge developer community\footnote{\emph{Android MVP} community:\\\url{https://plus.google.com/communities/114285790907815804707}} on \emph{Google+}, dealing with different MVP approaches. 
Finally, we want to draw your attention to the paper \emph{Android Passive MVC: a Novel Architecture Model for Android Application Development} \cite{PassiveMVC}, which is worth reading and has been an inspiration for our approach. Although the paper proposes an architecture which is rather MVC than MVP-based, 
it offers an interesting approach how the components of an \emph{Android} app can be organized for building an MV-x structure.
